Efficient Handling of String-Number Conversion

### 2020-03-31 final-version/evaluation.tex
fix table 1

\begin{table}[h]
\changed{
\centering
\caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on Basic String Constraint benchmarks.}
\scalebox{0.85}{
\begin{tabular}{|l r | r r r r |}
\hline
\multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3Str3 \\ \hline
\multirow{6}{*}{PyEx}		& SAT      & 21377& 19899& 16331&  3037 \\
							            & UNSAT    &  3860&  3848&  3831&  3830 \\
							            & UNKNOWN  &     0&     0&     0&     7 \\
							            & TIMEOUT  &  184&  1674&  5259& 16872 \\
							            & ERROR    &     0&     0&     0&  1675 \\
							            & INCORRECT&     0&     0&     0&    14 \\ \hline
%\multirow{6}{*}{APLAS}		& SAT      &   126&    51&    13&    35 \\
%							& UNSAT    &   286&   214&   100&   111 \\
%							& UNKNOWN  &     0&     0&     0&   345 \\
%							& TIMEOUT  &   188&   335&   487&    89 \\
%							& ERROR    &     0&     0&     0&    20 \\
%							& INCORRECT&     0&     0&     0&     0 \\ \hline
\multirow{6}{*}{LeetCode}	& SAT      &   877&   865&   881&   661 \\
							& UNSAT    &  1785&  1785&  1785&  1780 \\
							& UNKNOWN  &     0&     0&     0&   122 \\
							& TIMEOUT  &    0&    16&     0&    90 \\
							& ERROR    &     4&     0&     0&    13 \\
							& INCORRECT&     0&     0&     0&     0 \\ \hline
\multirow{6}{*}{StringFuzz}	& SAT      &   515&   704&   267&   505 \\
							& UNSAT    &   301&   245&   188&   192 \\
							& UNKNOWN  &     0&     0&     0&     4 \\
							& TIMEOUT  &   249&   116&   610&   364 \\
							& ERROR    &     0&     0&     0&     0 \\
							& INCORRECT&     0&     0&     0&     0 \\\hline
\multirow{6}{*}{cvc4\textsubscript{pred}} & SAT &    13&    11&    12&     8 \\
							& UNSAT    &   822&   818&   808&   774 \\
							& UNKNOWN  &     0&     0&     0&     4 \\
							& TIMEOUT  &     0&     6&    15&    38 \\
							& ERROR    &     0&     0&     0&     9 \\
							& INCORRECT&     0&     0&     0&     0 \\ \hline
\multirow{6}{*}{cvc4\textsubscript{term}} & SAT &    10&     8&     5&    16 \\
							& UNSAT    &  1032&  1025&  1022&   957 \\
							& UNKNOWN  &     0&     0&     0&     3 \\
							& TIMEOUT  &     3&    12&    18&    58 \\
							& ERROR    &     0&     0&     0&     8 \\
							& INCORRECT&     0&     0&     0&    14 \\ \hline \hline
\multirow{6}{*}{Total} 		& SAT      & 22792& 21487& 17496&  4227\\
							& UNSAT    &  7800&  7721&  7634&  7533\\
							& UNKNOWN  &     0&     0&     0&   140\\
							& TIMEOUT  &  437&  1824&  151& 17422 \\
							& ERROR    &     4&     0&     0&  1705 \\
							& INCORRECT&     0&     0&     0&    28 \\\hline
\end{tabular}}
\label{table:base_benchmark}}
\end{table}

>>>>

\begin{table}[h]
\changed{
\centering
\caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on Basic String Constraint benchmarks.}
\scalebox{0.85}{
\begin{tabular}{|l r | r r r r |}
\hline
\multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3Str3 \\ \hline
\multirow{6}{*}{PyEx}		& SAT      & 21377& 19899& 16331&  3037 \\
							            & UNSAT    &  3860&  3848&  3831&  3830 \\
							            & UNKNOWN  &     0&     0&     0&     7 \\
							            & TIMEOUT  &  184&  1674&  5259& 16872 \\
							            & ERROR    &     0&     0&     0&  1675 \\
							            & INCORRECT&     0&     0&     0&    14 \\ \hline
%\multirow{6}{*}{APLAS}		& SAT      &   126&    51&    13&    35 \\
%							& UNSAT    &   286&   214&   100&   111 \\
%							& UNKNOWN  &     0&     0&     0&   345 \\
%							& TIMEOUT  &   188&   335&   487&    89 \\
%							& ERROR    &     0&     0&     0&    20 \\
%							& INCORRECT&     0&     0&     0&     0 \\ \hline
\multirow{6}{*}{LeetCode}	& SAT      &   877&   865&   881&   661 \\
							& UNSAT    &  1785&  1785&  1785&  1780 \\
							& UNKNOWN  &     0&     0&     0&   122 \\
							& TIMEOUT  &    0&    16&     0&    90 \\
							& ERROR    &     4&     0&     0&    13 \\
							& INCORRECT&     0&     0&     0&     0 \\ \hline
\multirow{6}{*}{StringFuzz}	& SAT      &   515&   704&   267&   505 \\
							& UNSAT    &   301&   245&   188&   192 \\
							& UNKNOWN  &     0&     0&     0&     4 \\
							& TIMEOUT  &   249&   116&   610&   364 \\
							& ERROR    &     0&     0&     0&     0 \\
							& INCORRECT&     0&     0&     0&     0 \\\hline
\multirow{6}{*}{cvc4\textsubscript{pred}} & SAT &    13&    11&    12&     8 \\
							& UNSAT    &   822&   818&   808&   774 \\
							& UNKNOWN  &     0&     0&     0&     4 \\
							& TIMEOUT  &     0&     6&    15&    38 \\
							& ERROR    &     0&     0&     0&     9 \\
							& INCORRECT&     0&     0&     0&     0 \\ \hline
\multirow{6}{*}{cvc4\textsubscript{term}} & SAT &    10&     8&     5&    16 \\
							& UNSAT    &  1032&  1025&  1022&   957 \\
							& UNKNOWN  &     0&     0&     0&     3 \\
							& TIMEOUT  &     3&    12&    18&    58 \\
							& ERROR    &     0&     0&     0&     8 \\
							& INCORRECT&     0&     0&     0&    14 \\ \hline \hline
\multirow{6}{*}{Total} 		& SAT      & 22792& 21487& 17496&  4227\\
							& UNSAT    &  7800&  7721&  7634&  7533\\
							& UNKNOWN  &     0&     0&     0&   140\\
							& TIMEOUT  &  436&  1824&  5902& 17422 \\
							& ERROR    &     4&     0&     0&  1705 \\
							& INCORRECT&     0&     0&     0&    28 \\\hline
\end{tabular}}
\label{table:base_benchmark}}
\end{table}
